---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Floating Catchment Area (FCA) Methods

<!-- badges: start -->
[![R-CMD-check](https://github.com/egrueebler/fca/workflows/R-CMD-check/badge.svg)](https://github.com/egrueebler/fca/actions)
[![Codecov test coverage](https://codecov.io/gh/egrueebler/fca/branch/main/graph/badge.svg)](https://app.codecov.io/gh/egrueebler/fca/branch/main)
<!-- badges: end -->

Floating Catchment Area (FCA) methods to Calculate Spatial Accessibility.

Perform various floating catchment area methods to calculate a spatial accessibility index (SPAI) for demand point data. The distance matrix used for weighting is normalized in a preprocessing step using common functions (gaussian, gravity, exponential or logistic).

## Installation

You can install the released version of fca from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("fca")
```

And the development version from [GitHub](https://github.com/egrueebler/fca) with:

``` r
# install.packages("devtools")
devtools::install_github("egrueebler/fca")
```

## Example

This is a basic example which shows you how to calculate a SPAI for demand point data using FCA methods.

Create an example population, supply and distances:

```{r example}
# Population df with column for size
pop <- data.frame(
  orig_id = letters[1:10],
  size = c(100, 200, 50, 100, 500, 50, 100, 100, 50, 500)
)

# Supply df with column for capacity
sup <- data.frame(
  dest_id = as.character(1:3),
  capacity = c(1000, 200, 500)
)

# Distance matrix with travel times from 0 to 30
D <- matrix(
  runif(30, min = 0, max = 30),
  ncol = 10, nrow = 3, byrow = TRUE,
  dimnames = list(c(1:3), c(letters[1:10]))
)
D
```

Normalize distance matrix with gaussian function, apply a threshold of 20 minutes (to compute beta for the function) and formatting input data as named vectors for the FCA method (match IDs of distance weight matrix with demand and supply data).

```{r preprocess}
library(fca)

# Normalize distances
W <- dist_normalize(
  D,
  d_max = 20,
  imp_function = "gaussian", function_d_max = 0.01
)

# Ensure order of ids
pop <- pop[order(pop$orig_id), ]
sup <- sup[order(sup$dest_id), ]

# Named vectors
(p <- setNames(pop$size, as.character(pop$orig_id)))
(s <- setNames(sup$capacity, as.character(sup$dest_id)))
```

Apply FCA method on formatted input, get SPAI for each origin location (`p`):

```{r fca}
(spai <- spai_3sfca(p, s, W))
```

## References

* [Bauer, J., & Groneberg, D. A. (2016). Measuring Spatial Accessibility of Health Care Providers – Introduction of a Variable Distance Decay Function within the Floating Catchment Area (FCA) Method.](https://doi.org/10.1371/journal.pone.0159148)
* [Joerg, R., Lenz, N., Wetz, S., & Widmer, M. (2019). Ein Modell zur Analyse der Versorgungsdichte. Herleitung eines Index zur räumlichen Zugänglichkeit mithilfe von GIS und Fallstudie zur ambulanten Grundversorgung in der Schweiz.](https://www.obsan.admin.ch/de/publikationen/ein-modell-zur-analyse-der-versorgungsdichte)
