---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Floating Catchment Area (FCA) Methods

<!-- badges: start -->
[![R-CMD-check](https://github.com/egrueebler/fca/workflows/R-CMD-check/badge.svg)](https://github.com/egrueebler/fca/actions)
[![Codecov test coverage](https://codecov.io/gh/egrueebler/fca/branch/main/graph/badge.svg)](https://app.codecov.io/gh/egrueebler/fca/branch/main)
<!-- badges: end -->

Floating Catchment Area (FCA) methods to Calculate Spatial Accessibility.

**Text from DESCRIPTION**

## Installation

You can install the released version of fca from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("fca")
```

And the development version from [GitHub](https://github.com/egrueebler/fca) with:

``` r
# install.packages("devtools")
devtools::install_github("egrueebler/fca")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(fca)
## basic example code
```

## References

* [PaperA](doi)
* [PaperB](doi)
* [PaperC](doi)
